### 2024-02-28 sections/2homology.tex
Add files via upload

    That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both $\infty$-operads $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

@@

The bulk of the work is then to show that such an adjoint exists and to try to find more concrete forms of factorization homology that would be easier to compute with. Being a left Kan extension one guess on the side of computation would be that we can find its values via colimits, as is usual for pointwise left Kan extensions. Determining under which assumptions factorization homology, in both its forms, exists and is given by a colimit is one of the major results of \cite{af_fhtop} (for the smooth case) and \cite{aft_fhstrat} (for the stratified case). Specifically lemmas \cite[lem.2.16]{aft_fhstrat} and \cite[lem.2.17]{aft_fhstrat} are great encapsulations of all the conditions that are needed.

@@

\begin{proof}
    The first equivalence comes by inspection of the morphism spaces which are discrete in this particular case. Since $\mathsf{Assoc^{RL}}$ is also born of a discrete nature we only need to find a bijection of morphism spaces. By construction of $\mathsf{Assoc^{RL}}$ such a bijection is immediate.
\end{proof}

@@

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which for our purposes defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}.
\end{remark}

@@

\begin{remark}
    The two-sided bar construction here gives the left derived tensor product. We, however, do not make a notational distinction between this left derived tensor product and the standard one since we should be clear from context. The left derived version will always appear due to some two-sided bar construction. 
\end{remark}

@@

\begin{example}
    Checking the definitions we can see that evaluating basics $U \in \disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$ is the same as simply evaluating the disk with the disk algebra. This is simply because factorization homology is a left Kan extension.

@@

All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}. We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.

>>>>

    That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

@@

The bulk of the task is then to show that such an adjoint exists and to try to find more concrete forms of factorization homology that would be easier to compute with. Being a left Kan extension one guess on the side of computation would be that we can find its values via colimits, as is usual for pointwise left Kan extensions. Determining under which assumptions factorization homology, in both its forms, exists and is given by a colimit is one of the major results of \cite{af_fhtop} (for the smooth case) and \cite{aft_fhstrat} (for the stratified case). Specifically lemmas \cite[lem.2.16]{aft_fhstrat} and \cite[lem.2.17]{aft_fhstrat} are great encapsulations of all the conditions that are needed.

@@

\begin{proof}
    The first equivalence comes by inspection of the morphism spaces which are discrete in this particular case. Since $\mathsf{Assoc^{RL}}$ is also born of a discrete nature we only need to find a bijection of morphism spaces. By the construction of $\mathsf{Assoc^{RL}}$ such a bijection is immediate.
\end{proof}

@@

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

@@

\begin{remark}
    The two-sided bar construction here gives the left derived tensor product. We, however, do not make a notational distinction between this left derived tensor product and the standard one since it should be clear from context. The left derived version will always appear due to some two-sided bar construction. 
\end{remark}

@@

\begin{example}
    Checking the definitions we can see that evaluating basics $U \in \disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$ with factorization homology is the same as simply evaluating the disk with the disk algebra. This is simply because factorization homology is a left Kan extension.

@@

All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}. %We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.

### 2024-02-28 sections/3algebras.tex
Add files via upload

\begin{remark}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
        \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that we don't need to provide the morphisms $F(\{U\}, U)$, because they are equivalent to the identity morphism.

@@

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    We first observe that by definition the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \cref{lem:double_slice}

@@

\begin{remark}
    The key idea for the proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds. This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
\end{remark}

@@

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces. This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however only locally constant factorization algebras can detect the stratified structure, so in all other cases that we have considered the above functor is even an equivalence, and not just fully-faithful.
\end{remark}

@@

    One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$. Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold.} for factorization homology we get essential surjectivity because there are equivalences
    %
    \begin{equation}
        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
    \end{equation}
    %
    between objects of $\catC$. As argued in the proof of \cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras. In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

@@

\begin{proposition}\label{prop:R_gives_E1}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\simeq} \lcfa_{\mathbb{R}} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    What is left to show is the essential surjectivity of the functor. This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself. So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$ algebra as $A = F(\mathbb{R})$. The previous observation and the local constancy then force the value on each disk to be equivalent to this. The space of embeddings of two disks $\mathbb{R} \sqcup \mathbb{R} \xhookrightarrow{} \mathbb{R}$ is, up to homotopy, equivalent to two points, which provide exactly the multiplication map $ A \otimes A \rightarrow A$ of the algebra and its opposite multiplication.  Associativity, up to homotopy, comes about exactly because all embeddings of any number of disks can, up to homotopy, be factorized through the embedding of two disks at a time. As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$. Thus, we have constructed an $\mathbb{E}_1$-algebra from the given data, and the proposition holds.
\end{proof}

@@

\begin{proposition}\label{prop:hoint_gives_modules}
    There is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathbb{E}_1$-algebras together with a right module and locally constant factorization algebras on the half-open interval
    %
    \begin{equation}
        \mathsf{RMod}(\catC) \xrightarrow{\simeq} \lcfa_{\hoint} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    The proof goes along the same lines as the proof of \cref{prop:R_gives_E1}. We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$.
\end{proof}

@@

\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:
\end{remark}

\begin{proposition}\label{univ_env_for_En}
    Given a locally constant factorization algebra $F$ on $\mathbb{R}^n$, its universal enveloping algebra is given by $\int_{S^{n-1}} F$, i.e. there is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n}_{F} (\catC) \xrightarrow{\ \ \simeq \ \ } \mathsf{LMod}_{\int_{S^{n-1}} F} (\catC).
    \end{equation}
\end{proposition}

>>>>

\begin{remark}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
        \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.

@@

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \cref{lem:double_slice}

@@

\begin{remark}
    Intuitively, the key idea for the statement and proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds. This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$. The proof of \cite[prop.2.22]{af_primer} makes this precise, and the above proof transports that idea to the relative case.
\end{remark}

@@

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement). This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however only locally constant factorization algebras can detect the stratified structure, so in all other cases that we have considered the above functor is even an equivalence, and not just fully-faithful.
\end{remark}

@@

    One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$. Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
    %
    \begin{equation}
        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
    \end{equation}
    %
    between objects of $\catC$. As argued in the proof of \cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras. In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

@@

\begin{proposition}\label{prop:R_gives_E1}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    What is left to show is the essential surjectivity of the functor. This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself. So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$-algebra as $A = F(\mathbb{R})$. The previous observation and the local constancy then force the value on each disk to be equivalent to this. The space of embeddings of two disks $\mathbb{R} \sqcup \mathbb{R} \xhookrightarrow{} \mathbb{R}$ is, up to homotopy, equivalent to two points, which provide exactly the multiplication map $ A \otimes A \rightarrow A$ of the algebra and its opposite multiplication.  Associativity, up to homotopy, comes about exactly because all embeddings of any number of disks can, up to homotopy, be factorized through the embedding of two disks at a time. As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$. Thus, we have constructed an $\mathbb{E}_1$-algebra from the given data, and the proposition holds.
\end{proof}

@@

\begin{proposition}\label{prop:hoint_gives_modules}
    There is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathbb{E}_1$-algebras together with a right module and locally constant factorization algebras on the half-open interval
    %
    \begin{equation}
        \mathsf{RMod}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\hoint} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    The proof goes along the same lines as the proof of \cref{prop:R_gives_E1}. We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$, as a specified stratum of $\hoint$.
\end{proof}

@@

\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:

    \begin{proposition}\label{univ_env_for_En}
        Given a locally constant factorization algebra $F$ on $\mathbb{R}^n$, its universal enveloping algebra is given by $\int_{S^{n-1}} F$, i.e. there is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \mathsf{Mod}^{\mathbb{E}_n}_{F} (\catC) \xrightarrow{\ \ \simeq \ \ } \mathsf{LMod}_{\int_{S^{n-1}} F} (\catC).
        \end{equation}
    \end{proposition}
    %
    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \cref{thm:classif_disk_d_under_n*_alg}.
\end{remark}
